---
title: "Final Project Example"
author: "seayoung Park"
date: "2023-12-06"
output: html_document
---

```
 (linebreak)
---
 (linebreak) 
```
Three dashes creaste a horizontal line

you need to make a linebreak above and below the dashes. 



---


(Do you see the horizontal line with `---` ?)

---

#### RMD file and HTML file

* rmd file: this file. basically, `text file` using **markdown language**.
* html file: output of your rmd file. when you `knit`, this text file is compiled and produce a html file. 

In RStudio, if you press `ctrl`+`s` or `command`+ `s`, it saves **rmd** file, the text file your wre writing. 
If you want to reflect the new changed in your rmd file into html file, you need to `knit`. 
Think `knit` as a ''save the output file (here, html) and show me the file''.



---

##### Size of headers

# The biggest
## Very big
### Big
#### Somehow big
##### Last level

This is the normal sized body text. 
And This is the second sentence.

This is the normal sized body text. And This is the second sentence.

---

##### bullet point 

* bullet 1
* bullet 2

- bullet with dash
- bullet with dash
  - one level deeper
  
##### ordered list
1. ordered list
2. ordered list
2. third item


##### emphasize words


Let's make **this word** bold

Let's make *this word* italic

Let's make `this word` inline code 



This chunk would print out the messages for attaching the package.
```{r}
library(dplyr)
```


But this would not. in case of warnings for attacing package, you can use `warning=` option.

(you can select other options from the option button the the right corner of the code chunk)
```{r warning=FALSE}
library(ggplot2)
```



